%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Jordan Bartos}} 
  & Email : \href{mailto:bartosj@oregonstate.edu}{bartosj@oregonstate.edu}\\
  &\href{https://www.linkedin.com/in/jordanBartos/}{LinkedIn}\\ 
  & Mobile : 713-412-5491 \\\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelor of Science in Computer Science in progress;  GPA: 4.00}{January 2017 -- Present}
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in Biology;  GPA: 2.76}{August 2004 -- May 2009}\\
  \resumeSubHeadingListEnd
\hfill

%-----------EXPERIENCE-----------------
\section{Relevant Experience}
	\resumeSubHeadingListStart
		\resumeSubheading
     		 {Oregon State University}{Corvallis, OR}
     		 {Teaching Assistant - Intro to Computer Science}{January 2019 - Present}
     		 \resumeItemListStart
        	\resumeItem{Instructor}
       	   {Assist beginning students in learning the fundamentals of C++ programming.}
       	\resumeItem{Grader}
       	   {Read and evaluate students' code to provide meaningful feedback.}\\
     	 \resumeItemListEnd
      \resumeSubHeadingListEnd
\hfill

%-----------ADDITIONAL SKILLS-----------------
\section{Additional Skills and Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{Relevant Coursework}
      {Intro to CS I \& II, Computer Architecture and Assembly Language, Usability Engineering, Discrete Structures in CS, Data Structures, Web Development}
    \resumeSubItem{Currently Enrolled}
    	{Analysis of Algorithms, Software Engineering I}
      \resumeSubItem{BeaverHacks Winter 2018}
      {Won overall first place with a team of three for our C\textsuperscript{++} console journaling program, \href{https://github.com/jkbartos/rewind-revitalize}{Rewind Revitalize}.}
    
  \resumeSubHeadingListEnd
\hfill

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{ C\textsuperscript{++}, MASM}
    \resumeSubItem{Currently Learning}{JavaScript, HTML, CSS}
    \resumeSubItem{LaTeX}
      {Proficient in LaTeX to make basic documents.}
    \resumeSubItem{Git and Github}
    {basic proficiency in Git and Github}
  \resumeSubHeadingListEnd
 \hfill

%-----------ADDITIONAL EXPERIENCE-----------------
\section{Additional Experience}
  \resumeSubHeadingListStart
  
 \resumeSubheading
      {Nor'banks Sailing and Watersports}{Duck, NC}
      {Sailing Instructor}{June - September 2013}
      \resumeItemListStart
      		\resumeItem{Sailing instructor}
      		{Instructed adults in the operation of sailing dinghies and small catamarans.}
      		\resumeItem{Safety instructor}
      		{Gave presentations on the safe operation of small watercraft.}
      \resumeItemListEnd
      
      
    \resumeSubheading
      {HOSTS - Help One Student To Succeed}{Bryan, TX}
      {Volunteer Tutor}{May - August 2005}
      \resumeItemListStart
        \resumeItem{Math Tutor}
          {Tutored middle school students that were having trouble in math and critical thinking subjects.}\\
      \resumeItemListEnd

   


 \resumeSubheading
      {McCoy's Building Supply}{Bryan, TX}
      {Class C Truck Driver}{May 2017 - Present}
      \resumeItemListStart
      		\resumeItem{Forklift Operator}
      		{Safely operated forklifts to load and unload freight trucks.}
      		\resumeItem{Truck Driver}
      		{Delivered lumber and other building materials safely and efficiently.}
      \resumeItemListEnd
      
      
    \resumeSubheading
      {Veritas Wine and Bistro}{College Station, TX}
      {Chef de Tournant}{September 2014 - June 2015}
      \resumeItemListStart
        \resumeItem{Chef de Tournant}
          {Saute, fry, grill, mise stations}\\
      \resumeItemListEnd
 
      
      
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
